---
title: "DV_RProject2"
output: html_document
---

##DV Project 2

1) We found a data set (csv file) about Diabetes patients with thousands of rows of data. We then regiestered our data set type under the PROJECt_2DATA column using the "Register Your Project" link on the class website.

2) We loaded the CSV file into one of our Oracle accounts using a modified version of R_ETL.R.

3) We modified the query found in Titanic Analysis.R by changing the SQL statement and filled in one of our UTEids to build a data frame from our data.

```{r}
source("../01 Data/Data.R", echo = TRUE)
```

4) We wrangled the data in 3 interesting ways as follows:
a. Time in Hospital of a Patient vs Number of Medications (and if they were Readmitted or Not)
b. Age of Patient vs Average Number of Medications (with Race)
c. Age of Patient vs Average Number of Medications (with Gender)

```{r}
source("../02 Data Wrangling/DataWrangling.R", echo = TRUE)
```

5) From those wrangled sets of data we produced the following 3 plots/visualizations of the data:

```{r}
source("../03 Visualizations/Visualizations.R", echo = TRUE)
```